Computing Entropies With Nested Sampling

### 2017-03-15 paper/ms.tex
Algorithm placeholder

\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}

@@

@@

\conflictofinterests{Conflicts of Interest}
The authors declare no conflicts of interest.

>>>>

\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}

@@

\begin{algorithm}
\caption{Calculate $y = x^n$}
\begin{algorithmic} 
\REQUIRE $n \geq 0 \vee x \neq 0$
\ENSURE $y = x^n$
\STATE $y \leftarrow 1$
\IF{$n < 0$}
\STATE $X \leftarrow 1 / x$
\STATE $N \leftarrow -n$
\ELSE
\STATE $X \leftarrow x$
\STATE $N \leftarrow n$
\ENDIF
\WHILE{$N \neq 0$}
\IF{$N$ is even}
\STATE $X \leftarrow X \times X$
\STATE $N \leftarrow N / 2$
\ELSE[$N$ is odd]
\STATE $y \leftarrow y \times X$
\STATE $N \leftarrow N - 1$
\ENDIF
\ENDWHILE
\end{algorithmic}
\end{algorithm}

@@

\conflictofinterests{Conflicts of Interest}
The authors declare no conflicts of interJason Mamford Half of the money collected from the Northern Toll road is wasted in costs. It cost millions of dollars for one gantry, so how much for 50 gantries? How much for a million transponders? You see, nobody will tell us anything until it is too late.
est.
